---
title: "problem_set_4"
author: "Sara Orofino"
date: "3/3/2020"
output: pdf_document
---

```{r read-data, include=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(here)

climate <- read_csv(file=file.path(here(), "/data/sets_4_5/climate.csv"))
nuclear <- read_csv(file=file.path(here(), "/data/sets_4_5/nuclear.csv"))
crab1 <- read_csv(file=file.path(here(), "/data/sets_4_5/crab1.csv"))
crab2 <- read_csv(file=file.path(here(), "/data/sets_4_5/crab2.csv"))
upwell <- read_csv(file=file.path(here(), "/data/sets_4_5/upwell.csv"))

```

#Question 1

##Effects of climate change on marine ecosystems

**Goal:**Provide evidence for changes in marine communities that may be due to climatic changes, such as increases in temperature.  

Start by looking at the following information for all species:
 * The mode of development (i.e., planktonic larvae vs. non-planktonic larvae)   
 * The geographic range (i.e., does the species range occur primarily North or South of the site, or is it Cosmopolitan - both north
and south)  
* The trophic level (i.e., predator, filter feeder, scavenger)   

Questions to consider:  
 * What are the patterns of change?  
 * Try grouping the species by categories and see if anything emerges.  

Visualizing the data by looking at the change in density as a function of the mode of development:   
```{r climate-mode, echo=FALSE}

mode <- ggplot(climate, aes(x=species, y=density, fill = development)) + 
  geom_col() + 
  scale_fill_manual(breaks = c("non-planktonic", "planktonic"), values = c("turquoise3", "navyblue"),
                     labels = c("Non-planktonic", "Planktonic"), name = "") + 
  labs(x = "Species", y = "Change in Density", title = "Change in Density by Mode of Development") +
  theme_bw()
mode
```
 From this graph we can see that negative and positive density changes are not necessarily dependent on development type. Some planktonic modes of development are increasing density while otheers are decreasing density. The same is also true for non-planktonic modes of development.  
 
Density changes by geographic location:  
```{r climate-geography, echo=FALSE}
geography <- ggplot(climate, aes(x=species, y=density, fill = range)) + 
  geom_col() + 
  scale_fill_manual(values = c("slategrey", "navyblue", "turquoise3"),
                    name = "") + 
  labs(x = "Species", y = "Change in Density", title = "Change in Density by Geographic Location") +
  theme_bw()
geography
```
From this graph we can see that species located in the north tend to have declining densities (negative change), while those species in the south are seeing positive density change. Cosmopolitan areas are having mostly positive density changes, although this is not the case across the board.  

Density changes by tropic level:  
```{r climate-trophic, echo=FALSE}
trophic <- ggplot(climate, aes(x=species, y=density, fill = trophic)) + 
  geom_col() + 
  scale_fill_manual(values = c("seagreen4", "navyblue", "turquoise3"),
                    labels = c("Filter Feeder", "Predator", "Scavenger"),
                    name = "") + 
  labs(x = "Species", y = "Change in Density", title = "Change in Density by Trophic Level") +
  theme_bw()
trophic
```
From this graph there doesn't appear to be a relationship between the change in density and the trophic level. At all three trophic levels there are some species which are increasing in density and some that are decreasing in density.  

Linear Regression:
```{r climate-regression}
geog_model <- lm(formula = density ~ range + development + trophic, data=climate)
summary(geog_model)
```


#Question 2 

##Effects of a nuclear power plant

**Goal:**Determine if there are any detectable impacts of the plants on the three invertebrate species.  

Sites:  
 * Discharge point (10 years before and 10 years after)  
 * Hyperion Bay (10 years before and 10 years after)  
 * Noway Bay (10 years before and 10 years after)  

Start by visualizing the pattern in the three sites together:  
```{r nuclear-plot1, echo=FALSE}
nuc_point <- ggplot(nuclear, aes(x=year, y=density)) + 
  geom_point(aes(color = species)) + 
  facet_wrap(~location)
nuc_point

nuc_line <- ggplot(nuclear, aes(x=year, y=density)) + 
  geom_line(aes(color = species)) + 
  facet_wrap(~location)
nuc_line

#Make a plot of all three species at Diablo for HW5:
diablo <- nuclear %>%
  filter(location == "diablo")

diablo_plot <- ggplot(diablo, aes(x = year, y=density, color=species)) + 
  geom_line(alpha = 0.7) + 
  geom_vline(xintercept = 2010) + 
  geom_smooth(method = "lm", formula = y ~ x, aes(color = species), se = FALSE, size = 0.8) +
  scale_color_manual(values = c("darkorange", "darkcyan", "forestgreen"),
                     labels = c("A", "B", "C"),
                     name = "Species") + 
  scale_y_continuous(limits = c(0,30), breaks = seq(0,30,10)) +
  scale_x_continuous(limits =c(2000,2020), breaks = seq(2000,2020,5), expand = c(0,0)) +
  labs(x = "Year", y = "Change in Density",
       title = "Change in Density Over Time",
       subtitle = "Diablo Cove") + 
  theme_bw()
diablo_plot
  
```
 Diablo: Species A remains similar (increases a little maybe), Species B declines, Species C increases  
 Hyperion: Species A remains similar, Species B declines, Species C increases  
 Noway: Species A similar (maybe decreases a little), Species B declines, Species C increases  
 
 Line Charts by Species:  
 
 **Species A**  
```{r spp-a, echo=FALSE}
spp_a <- nuclear %>% 
  filter(species == "A")

spp_a_graph <- ggplot(spp_a, aes(x = year, y=density, color=location)) + 
  geom_line(alpha = 0.7) + 
  geom_vline(xintercept = 2010) + 
  geom_smooth(method = "lm", formula = y ~ x, aes(color = location), se = FALSE, size = 0.8) +
  scale_color_manual(values = c("darkgreen", "darkgoldenrod", "indianred4"),
                     labels = c("Diablo", "Hyperion", "Noway"),
                     name = "Monitoring Site") + 
  scale_y_continuous(limits = c(0,30), breaks = seq(0,30,10)) +
  scale_x_continuous(limits =c(2000,2020), breaks = seq(2000,2020,5), expand = c(0,0)) + 
  labs(x = "Year", y = "Change in Density",
       title = "Change in Density Over Time",
       subtitle = "Species A") + 
  theme_bw()
spp_a_graph
```
Species A remains relatively constant at all the sites   
 
**Species B**  
```{r spp-b, echo=FALSE}
spp_b <- nuclear %>% 
  filter(species == "B")

spp_b_graph <- ggplot(spp_b, aes(x = year, y=density, color=location)) + 
  geom_line(alpha = 0.7) + 
  geom_vline(xintercept = 2010) + 
  geom_smooth(method = "lm", formula = y ~ x, aes(color = location), se = FALSE, size = 0.8) + 
  scale_color_manual(values = c("darkgreen", "darkgoldenrod", "indianred4"),
                     labels = c("Diablo", "Hyperion", "Noway"),
                     name = "Monitoring Site") + 
  scale_y_continuous(limits = c(0,30), breaks = seq(0,30,10)) +
  scale_x_continuous(limits =c(2000,2020), breaks = seq(2000,2020,5), expand = c(0,0)) + 
  labs(x = "Year", y = "Change in Density",
       title = "Change in Density Over Time",
       subtitle = "Species B") + 
  theme_bw()
spp_b_graph
```
Species B decreases at all thre sites relative to the pre-power plant monitoring  

**Species C**  
```{r spp-c, echo=FALSE}
spp_c <- nuclear %>% 
  filter(species == "C")

spp_c_graph <- ggplot(spp_c, aes(x = year, y=density, color=location)) + 
  geom_line(alpha = 0.7) + 
  geom_vline(xintercept = 2010) + 
  geom_smooth(method = "lm", formula = y ~ x, aes(color = location), se = FALSE, size = 0.8) +
  scale_color_manual(values = c("darkgreen", "darkgoldenrod", "indianred4"),
                     labels = c("Diablo", "Hyperion", "Noway"),
                     name = "Monitoring Site") + 
  scale_y_continuous(limits = c(0,30), breaks = seq(0,30,10)) +
  scale_x_continuous(limits =c(2000,2020), breaks = seq(2000,2020,5), expand = c(0,0)) + 
  labs(x = "Year", y = "Change in Density",
       title = "Change in Density Over Time",
       subtitle = "Species C") + 
  theme_bw()
spp_c_graph
```
Species C increases at all three sites relative to pre-power plant monitoring   

#Question 3

##Managing a new fishery to halt invasive species

Main issues with previous approaches to manage crab fishery:  

Limitations of prior attempts to predict recruitment solely on the basis of the # of adults are:  
 * The predictions ignore the fact that the species have open populations (i.e., they have large scale larval
dispersal so that recruits may come from somewhere else -- like CA adults coming from OR recruits)  
 * The predictions ignore environmental variation affecting adults (e.g., food supply, predators)  
 * The predictions ignore environmental variation affecting the success of larvae during their development (e.g., food supply, temperature, and predator abundances)  

*Key Points*  
 * This time of year currents run north to south along the shore (could be moving larvae from OR to CA)   
 * crab larvae live about 3 weeks before settling but barnacle larvae live only 10 days  
 * both species spawn in the spring  
 * barnacles are immobile and filter phytoplankton from the water column; crabs are scavengers and eat detritus from seafloor 
  - barnacles may be more sensitive to a lack of food because they can't move
 
*Upwelling*  
Large positive values imply strong upwelling (and abundant nutrients and phytoplankton). Negative values imply downwelling (and low nutrients and rare phytoplankton). You obtain values for the summer, when juveniles are developing and for the winter, when adults are producing new eggs. Remember, values affecting adults are for different years than values affecting larvae.  

*Steps*  
Try plotting the recruitment data against the other variables that might be able to explain them. Use a scatterplot. Look for patterns (e.g., straight lines or smooth curves) that imply there is a relationship between the variable and the pattern of recruitment.  


Start with scatterplots to start seeing relationships in adult vs. recruits for crabs: 
```{r crab-plots, echo = FALSE}
#adult vs. crab recruitment CA
crab_1 <- ggplot(crab2, aes(x = crab_ca_ad, y = crab_ca_rec)) +
  geom_point(aes(color = year)) +
  theme_bw()
crab_1


#adult vs. crab recruitment OR:
crab_2 <- ggplot(crab2, aes(x = crab_or_ad, y = crab_or_rec)) +
  geom_point(aes(color = year)) +
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size = 0.5) + 
  theme_bw()
crab_2
#no pattern

#adult ca vs. recruit or crab
crab_3 <- ggplot(crab2, aes(x = crab_ca_ad, y = crab_or_rec)) +
  geom_point(aes(color = as.factor(year))) +
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) +
  theme_light()
crab_3
#no pattern

#oregon adult vs. california rec.
crab_4 <- ggplot(crab1, aes(x = crab_or_ad, y = crab_ca_rec)) +
  geom_point(aes(color = as.factor(year))) +
  scale_x_continuous(limits = c(0,50)) + 
  scale_y_continuous(limits = c(0,50)) +
  theme_light()
crab_4

#Adult crab vs. adult barnacle in CA and OR:
crab_5 <- ggplot(crab1, aes(x = crab_ca_ad, y = barnacle_ca_ad)) +
  geom_point(aes(color = as.factor(year))) +
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) +
  theme_light()
crab_5
```

Crab densities and upwelling:  
```{r crab-upwelling, echo=FALSE}
#Adults vs. summer upwelling in CA and OR  
summer_ca <- ggplot(crab1, aes(x = summer_ca, y = crab_ca_ad)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
summer_ca

summer_or <- ggplot(crab1, aes(x = summer_or, y = crab_or_ad)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
summer_or
#Decent relationships

#Recruits (in 2001) vs. summer upwelling in CA and OR (2000)
summer_ca_rec <- ggplot(crab1, aes(x = crab_ca_rec, y = summer_ca)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
summer_ca_rec

summer_or_rec <- ggplot(crab1, aes(x = crab_or_rec, y = summer_or)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
summer_or_rec
#Neither have much of a relationship

#Recruits(2001) vs. summer upwelling in CA and OR (2001):
summer_ca_rec2 <- ggplot(crab2, aes(x = crab_ca_rec, y = summer_ca)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
summer_ca_rec2

summer_or_rec2 <- ggplot(crab2, aes(x = crab_or_rec, y = summer_or)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
summer_or_rec2
#Neither are very strong 

#Adults vs. winter upwelling in CA and OR
winter_ca <- ggplot(crab1, aes(x = crab_ca_ad, y = winter_ca)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
winter_ca
#negative but not too strong

winter_or <- ggplot(crab1, aes(x = crab_or_ad, y = winter_or)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
winter_or
#not too strong

#Recruits (2001) vs. winter upwelling in CA and OR (2000):
winter_ca_rec <- ggplot(crab1, aes(x = crab_ca_rec, y = winter_ca)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
winter_ca_rec
#not much of a relationship

winter_or_rec <- ggplot(crab1, aes(x = crab_or_rec, y = winter_or)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
winter_or_rec
#also not much of a relationship

#Recruits (2001) vs. winter upwelling in CA and OR (2001):
winter_ca_rec2 <- ggplot(crab2, aes(x = crab_ca_rec, y = winter_ca)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
winter_ca_rec2
#decent negative relationship

winter_or_rec2 <- ggplot(crab2, aes(x = crab_or_rec, y = winter_or)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
winter_or_rec2
#not much of a relationship
```

Barnacle adult vs. recruit densities:
```{r barnacle-plots}
#adult vs. barnacle recruitment CA
b_1 <- ggplot(crab2, aes(x = barnacle_ca_ad, y = barnacle_ca_rec)) +
  geom_point(aes(color = year)) +
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size = 0.5) +
  scale_x_continuous(limits = c(0,50)) + 
  scale_y_continuous(limits = c(0,50)) +
  theme_bw()
b_1


#adult vs. barnacle recruitment OR:
b_2 <- ggplot(crab2, aes(x = barnacle_or_ad, y = barnacle_or_rec)) +
  geom_point(aes(color = year)) +
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size = 0.5) + 
  theme_bw()
b_2
#no pattern

#adult ca vs. recruit or barnacle
b_3 <- ggplot(crab2, aes(x = barnacle_ca_ad, y = barnacle_or_rec)) +
  geom_point(aes(color = year)) +
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) +
  theme_light()
b_3
#no pattern

#oregon adult vs. california rec.
b_4 <- ggplot(crab2, aes(x = barnacle_or_ad, y = barnacle_ca_rec)) +
  geom_point(aes(color=year)) +
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) +
  scale_x_continuous(limits = c(0,50)) + 
  scale_y_continuous(limits = c(0,50)) +
  theme_light()
b_4
```



Barnacle densities and upwelling: 
```{r barnacle-upwelling, echo=FALSE}
#Adults vs. summer upwelling in CA and OR  
b_summer_ca <- ggplot(crab1, aes(x = barnacle_ca_ad, y = summer_ca)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
b_summer_ca
#not great

b_summer_or <- ggplot(crab1, aes(x = barnacle_or_ad, y = summer_or)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
b_summer_or
#not great either

#Recruits (2001) vs. summer upwelling in CA and OR (2000)
b_summer_ca_rec <- ggplot(crab1, aes(x = barnacle_ca_rec, y = summer_ca)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
b_summer_ca_rec
#ehh

b_summer_or_rec <- ggplot(crab1, aes(x = summer_or, y = barnacle_or_rec)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
b_summer_or_rec
#This one is strong

#Recruits (2001) vs. summer upwelling in CA and OR (2001)
b_summer_ca_rec2 <- ggplot(crab2, aes(x = barnacle_ca_rec, y = summer_ca)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
b_summer_ca_rec2
#maybe

b_summer_or_rec2 <- ggplot(crab2, aes(x = barnacle_or_rec, y = summer_or)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
b_summer_or_rec2
#no real relationship

#Adults vs. winter upwelling in CA and OR
b_winter_ca <- ggplot(crab1, aes(x = barnacle_ca_ad, y = winter_ca)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
b_winter_ca
#decently strong

b_winter_or <- ggplot(crab1, aes(x = barnacle_or_ad, y = winter_or)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
b_winter_or
#not too strong

#Recruits (2001) vs. winter upwelling in CA and OR (2000)
b_winter_ca_rec <- ggplot(crab1, aes(x = barnacle_ca_rec, y = winter_ca)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
b_winter_ca_rec
#not much of a relationship

b_winter_or_rec <- ggplot(crab1, aes(x = barnacle_or_rec, y = winter_or)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
b_winter_or_rec
#also not much of a relationship

#Recruits (2001) vs. winter upwelling in CA and OR (2001)
b_winter_ca_rec2 <- ggplot(crab2, aes(x = winter_ca, y = barnacle_ca_rec)) + 
  geom_point(aes(color = as.factor(year))) + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
b_winter_ca_rec2
#very strong

b_winter_or_rec2 <- ggplot(crab2, aes(x = winter_or, y = barnacle_or_rec)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
b_winter_or_rec2
#not much of a relationship

#Recruits might be coming from OR to CA with currents so maybe 
```

The three relationships that seem decently strong are:  
 * CA barnacle adult densities (year x) vs. ca recruit densities (year x+1)  
 * CA adult crab densities vs. ca summer upwelling (same year)     
 * OR adult crab densities vs. or summer upwelling (same year)  
 * OR barnacle recruits vs. summer upwelling  (same year)  
 * CA adult barnacles vs. winter upwelling  (same year)  
 * CA barnacle recruits (year x+1) vs. winter upwelling (year x)
 
Try a regression for these relationships to see if they are significant:  
```{r}
#ca crab adult vs. barnacle adult density:
crab_b_ad <- lm(formula = crab_ca_ad ~ barnacle_ca_ad, data = crab1)
summary(crab_b_ad) #significant 0.003

#adult barnacle density vs recruits
ca_b_ad <- lm(formula = barnacle_ca_rec ~ barnacle_ca_ad, data = crab1)
summary(ca_b_ad) #significant at 0.002

#ca adults vs. summer upwelling (same year)
ca_ad_up <- lm(formula = crab_ca_ad ~ summer_ca, data=crab1)
summary(ca_ad_up) #significant at 0.06

#or adults vs. summer upwelling (same year)
or_ad_up <- lm(formula = crab_or_ad ~ summer_or, data=crab1)
summary(or_ad_up) #significant at 0.009

#or barnacle recruits (year x+1) vs. summer upwelling (year x)
or_b_rec_up <- lm(formula = barnacle_or_rec ~ summer_or, data=crab1)
summary(or_b_rec_up) #highly significant < 0.0001

#ca adult barnacles vs. winter upwelling
ca_b_ad_up <- lm(formula = barnacle_ca_ad ~ winter_ca, data=crab1)
summary(ca_b_ad_up) #also very significant 0.0006

#ca recruits (year x+1) vs. winter upwelling (year x)
ca_b_rec_up <- lm(formula = barnacle_ca_rec ~ winter_ca, data=crab1)
summary(ca_b_rec_up) #significant 0.072

```


Plots for paper to make look nicer:
```{r final-plots}
#Barnacle densities (adult vs. recruit) in CA:
b_1 <- ggplot(crab1, aes(x = barnacle_ca_ad, y = barnacle_ca_rec)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size = 0.5) +
  labs(x = "Adult Barnacle Density (Year X)",
       y = "Barnacle Recruit Density (Year X+1)",
       title = "California Barnacle Adult vs. Recruit Densities") +
  scale_x_continuous(limits = c(25,45)) + 
  scale_y_continuous(limits = c(0,20)) +
  theme_bw()
b_1

# ca adults vs summer upwelling
summer_ca <- ggplot(crab1, aes(x = summer_ca, y = crab_ca_ad)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  labs(x = "Summer Upwelling Index",
       y = "Adult Crab Densities",
       title = "California Adult Crab Densities vs. Summer Upwelling Index") +
  scale_x_continuous(expand = c(0.05,0.05)) + 
  scale_y_continuous(limits = c(0,50), breaks = seq(0,50,10)) +
  theme_bw()
summer_ca

# or adult vs. summer upwelling
summer_or <- ggplot(crab1, aes(x = summer_or, y = crab_or_ad)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  labs(x = "Summer Upwelling Index",
       y = "Adult Crab Densities",
       title = "Oregon Adult Crab Densities vs. Summer Upwelling Index") +
  scale_x_continuous(expand = c(0.05,0.05)) + 
  scale_y_continuous(limits = c(0,50), breaks = seq(0,50,10)) +
  theme_bw()
summer_or

#Maybe include this bell curve between or adults and ca recruits:
crab_4 <- ggplot(crab1, aes(x = crab_or_ad, y = crab_ca_rec)) +
  geom_point() +
  theme_bw()
crab_4

#CA barnacle adults vs. winter upwelling
b_winter_ca <- ggplot(crab1, aes(x = winter_ca, y = barnacle_ca_ad)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  labs(x = "Winter Upwelling Index",
       y = "Adult Barnacle Densities",
       title = "California Adult Barnacle Densities vs. Winter Upwelling Index") +
  scale_x_continuous(expand = c(0.05,0.05)) +  
  scale_y_continuous(limits = c(0,50), breaks = seq(0,50,10)) +
  theme_bw()
b_winter_ca

#CA crab recruits (year x+1) vs. winter upwelling in CA (year x):
winter_ca_rec2 <- ggplot(crab1, aes(x = winter_ca, y = crab_ca_rec)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  labs(x = "Winter Upwelling Index (Year X)",
       y = "Crab Recruit Densities (Year X)",
       title = "California Crab Recruit Densities vs. Winter Upwelling Index") +
  scale_x_continuous(expand = c(0.05,0.05)) + 
  scale_y_continuous(limits = c(0,50), breaks = seq(0,50,10)) +
  theme_bw()
winter_ca_rec2

#OR barnacle recruits (year x+1) vs. summer upwelling in OR (year x)
b_summer_or_rec <- ggplot(crab1, aes(x = summer_or, y = barnacle_or_rec)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  labs(x = "Summer Upwelling Index (Year X)",
       y = "Barnacle Recruit Densities (Year X+1)",
       title = "Oregon Barnacle Recruit Densities vs. Summer Upwelling Index") +
  scale_x_continuous(expand = c(0.05,0.05)) + 
  scale_y_continuous(limits = c(0,50), breaks = seq(0,50,10)) +
  theme_bw()
b_summer_or_rec

#CA barnacle recruits (year x+1) vs. winter upwelling in CA (year x)
b_winter_ca_rec2 <- ggplot(crab1, aes(x = winter_ca, y = barnacle_ca_rec)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  labs(x = "Winter Upwelling Index (Year X)",
       y = "Barnacle Recruit Densities (Year X+1)",
       title = "California Barnacle Recruit Densities vs. Winter Upwelling Index") +
  scale_x_continuous(expand = c(0.05,0.05)) + 
  scale_y_continuous(limits = c(0,50), breaks = seq(0,50,10)) +
  theme_bw()
b_winter_ca_rec2

#Adult crabs vs. adult barnacles in CA (same year)
crab_5 <- ggplot(crab1, aes(x = crab_ca_ad, y = barnacle_ca_ad)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) +
  labs(x = "Crab Adult Density",
       y = "Barnacle Adult Density",
       title = "California Barnacle and Crab Adult Densities") +
  scale_x_continuous(expand = c(0.05,0.05)) + 
  scale_y_continuous(limits = c(20,50), breaks = seq(20,50,10), expand = c(0,0)) +
  theme_light()
crab_5
```

