---
title: "problem_set_4"
author: "Sara Orofino"
date: "3/3/2020"
output: pdf_document
---

```{r read-data, include=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(here)

climate <- read_csv(file=file.path(here(), "/data/sets_4_5/climate.csv"))
nuclear <- read_csv(file=file.path(here(), "/data/sets_4_5/nuclear.csv"))
crab <- read_csv(file=file.path(here(), "/data/sets_4_5/crab.csv"))
upwell <- read_csv(file=file.path(here(), "/data/sets_4_5/upwell.csv"))

```

#Question 1

##Effects of climate change on marine ecosystems

**Goal:**Provide evidence for changes in marine communities that may be due to climatic changes, such as increases in temperature.  

Start by looking at the following information for all species:
 * The mode of development (i.e., planktonic larvae vs. non-planktonic larvae)   
 * The geographic range (i.e., does the species range occur primarily North or South of the site, or is it Cosmopolitan - both north
and south)  
* The trophic level (i.e., predator, filter feeder, scavenger)   

Questions to consider:  
 * What are the patterns of change?  
 * Try grouping the species by categories and see if anything emerges.  

Visualizing the data by looking at the change in density as a function of the mode of development:   
```{r climate-mode, echo=FALSE}

mode <- ggplot(climate, aes(x=species, y=density, fill = development)) + 
  geom_col() + 
  scale_fill_manual(breaks = c("non-planktonic", "planktonic"), values = c("turquoise3", "navyblue"),
                     labels = c("Non-planktonic", "Planktonic"), name = "") + 
  labs(x = "Species", y = "Change in Density", title = "Change in Density by Mode of Development") +
  theme_bw()
mode
```
 From this graph we can see that negative and positive density changes are not necessarily dependent on development type. Some planktonic modes of development are increasing density while otheers are decreasing density. The same is also true for non-planktonic modes of development.  
 
Density changes by geographic location:  
```{r climate-geography, echo=FALSE}
geography <- ggplot(climate, aes(x=species, y=density, fill = range)) + 
  geom_col() + 
  scale_fill_manual(values = c("slategrey", "navyblue", "turquoise3"),
                    name = "") + 
  labs(x = "Species", y = "Change in Density", title = "Change in Density by Geographic Location") +
  theme_bw()
geography
```
From this graph we can see that species located in the north tend to have declining densities (negative change), while those species in the south are seeing positive density change. Cosmopolitan areas are having mostly positive density changes, although this is not the case across the board.  

Density changes by tropic level:  
```{r climate-trophic, echo=FALSE}
trophic <- ggplot(climate, aes(x=species, y=density, fill = trophic)) + 
  geom_col() + 
  scale_fill_manual(values = c("seagreen4", "navyblue", "turquoise3"),
                    labels = c("Filter Feeder", "Predator", "Scavenger"),
                    name = "") + 
  labs(x = "Species", y = "Change in Density", title = "Change in Density by Trophic Level") +
  theme_bw()
trophic
```
From this graph there doesn't appear to be a relationship between the change in density and the trophic level. At all three trophic levels there are some species which are increasing in density and some that are decreasing in density.  

Linear Regression:
```{r climate-regression}
geog_model <- lm(formula = density ~ range + development + trophic, data=climate)
summary(geog_model)
```


#Question 2 

##Effects of a nuclear power plant

**Goal:**Determine if there are any detectable impacts of th eplants on the three invertebrate species.  

Sites:  
 * Discharge point (10 years before and 10 years after)  
 * Hyperion Bay (10 years before and 10 years after)  
 * Noway Bay (10 years before and 10 years after)  

Start by visualizing the pattern in the three sites together:  
```{r nuclear-plot1, echo=FALSE}
nuc_point <- ggplot(nuclear, aes(x=year, y=density)) + 
  geom_point(aes(color = species)) + 
  facet_wrap(~location)
nuc_point

nuc_line <- ggplot(nuclear, aes(x=year, y=density)) + 
  geom_line(aes(color = species)) + 
  facet_wrap(~location)
nuc_line
```
 Diablo: Species A remains similar (increases a little maybe), Species B declines, Species C increases  
 Hyperion: Species A remains similar, Species B declines, Species C increases  
 Noway: Species A similar (maybe decreases a little), Species B declines, Species C increases  
 
 Line Charts by Species:  
 
 **Species A**  
```{r spp-a, echo=FALSE}
spp_a <- nuclear %>% 
  filter(species == "A")

spp_a_graph <- ggplot(spp_a, aes(x = year, y=density, color=location)) + 
  geom_line(alpha = 0.7) + 
  geom_vline(xintercept = 2010) + 
  geom_smooth(method = "lm", formula = y ~ x, aes(color = location), se = FALSE, size = 0.8) +
  scale_color_manual(values = c("darkgreen", "darkgoldenrod", "indianred4"),
                     labels = c("Diablo", "Hyperion", "Noway"),
                     name = "Monitoring Site") + 
  scale_y_continuous(limits = c(0,30), breaks = seq(0,30,10)) +
  scale_x_continuous(limits =c(2000,2020), breaks = seq(2000,2020,5), expand = c(0,0)) + 
  labs(x = "Year", y = "Change in Density",
       title = "Change in Density Over Time",
       subtitle = "Species A") + 
  theme_bw()
spp_a_graph
```
Species A remains relatively constant at all the sites   
 
**Species B**  
```{r spp-b, echo=FALSE}
spp_b <- nuclear %>% 
  filter(species == "B")

spp_b_graph <- ggplot(spp_b, aes(x = year, y=density, color=location)) + 
  geom_line(alpha = 0.7) + 
  geom_vline(xintercept = 2010) + 
  geom_smooth(method = "lm", formula = y ~ x, aes(color = location), se = FALSE, size = 0.8) + 
  scale_color_manual(values = c("darkgreen", "darkgoldenrod", "indianred4"),
                     labels = c("Diablo", "Hyperion", "Noway"),
                     name = "Monitoring Site") + 
  scale_y_continuous(limits = c(0,30), breaks = seq(0,30,10)) +
  scale_x_continuous(limits =c(2000,2020), breaks = seq(2000,2020,5), expand = c(0,0)) + 
  labs(x = "Year", y = "Change in Density",
       title = "Change in Density Over Time",
       subtitle = "Species B") + 
  theme_bw()
spp_b_graph
```
Species B decreases at all thre sites relative to the pre-power plant monitoring  

**Species C**  
```{r spp-c, echo=FALSE}
spp_c <- nuclear %>% 
  filter(species == "C")

spp_c_graph <- ggplot(spp_c, aes(x = year, y=density, color=location)) + 
  geom_line(alpha = 0.7) + 
  geom_vline(xintercept = 2010) + 
  geom_smooth(method = "lm", formula = y ~ x, aes(color = location), se = FALSE, size = 0.8) +
  scale_color_manual(values = c("darkgreen", "darkgoldenrod", "indianred4"),
                     labels = c("Diablo", "Hyperion", "Noway"),
                     name = "Monitoring Site") + 
  scale_y_continuous(limits = c(0,30), breaks = seq(0,30,10)) +
  scale_x_continuous(limits =c(2000,2020), breaks = seq(2000,2020,5), expand = c(0,0)) + 
  labs(x = "Year", y = "Change in Density",
       title = "Change in Density Over Time",
       subtitle = "Species C") + 
  theme_bw()
spp_c_graph
```
Species C increases at all three sites relative to pre-power plant monitoring   

#Question 3

##Managing a new fishery to halt invasive species

Main issues with previous approaches to manage crab fishery:  

Limitations of prior attempts to predict recruitment solely on the basis of the # of adults are:  
 * The predictions ignore the fact that the species have open populations (i.e., they have large scale larval
dispersal so that recruits may come from somewhere else)  
 * The predictions ignore environmental variation affecting adults (e.g., food supply, predators)  
 * The predictions ignore environmental variation affecting the success of larvae during their development (e.g., food supply, temperature, and predator abundances)  

*Key Points*  
 * This time of year currents run north to south along the shore  
 * crab larvae live about 3 weeks before settling but barnacle larvae live only 10 days  
 * both species spawn in the spring  
 * barnacles are scavengers and filter phytoplankton from the water column; crabs are scavengers and eat detritus from seafloor  
 
*Upwelling*  
Large positive values imply strong upwelling (and abundant nutrients and phytoplankton). Negative values imply downwelling (and low nutrients and rare phytoplankton). You obtain values for the summer, when juveniles are developing and for the winter, when adults are producing new eggs. Remember, values affecting adults are for different years than values affecting larvae.  

*Steps*  
Try plotting the recruitment data against the other variables that might be able to explain them. Use a scatterplot. Look for patterns (e.g., straight lines or smooth curves) that imply there is a relationship between the variable and the pattern of recruitment.  


Start with scatterplots to start seeing relationships:  
```{r crab-plots, echo = FALSE}
#adult vs. crab recruitment CA
crab_1 <- ggplot(crab, aes(x = crab_ca_rec, y = crab_ca_ad)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size = 0.5) + 
  theme_light()
crab_1
#no pattern

#adult vs. crab recruitment OR:
crab_2 <- ggplot(crab, aes(x = crab_or_rec, y = crab_or_ad)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size = 0.5) + 
  theme_light()
crab_2
#no pattern

#adult ca vs. recruit or crab
crab_3 <- ggplot(crab, aes(x = crab_or_rec, y = crab_ca_ad)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) +
  theme_light()
crab_3
#no pattern

#oregon adult vs. california rec.
crab_4 <- ggplot(crab, aes(x = crab_or_ad, y = crab_ca_rec)) +
  geom_point() +
  theme_light()
crab_4
#Interesting bell curve
```

Crab densities and upwelling:  
```{r crab-upwelling, echo=FALSE}
#Adults vs. summer upwelling in CA and OR  
summer_ca <- ggplot(crab, aes(x = crab_ca_ad, y = summer_ca)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
summer_ca

summer_or <- ggplot(crab, aes(x = crab_or_ad, y = summer_or)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
summer_or
#Decent relationships

#Recruits vs. summer upwelling in CA and OR
summer_ca_rec <- ggplot(crab, aes(x = crab_ca_rec, y = summer_ca)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
summer_ca_rec

summer_or_rec <- ggplot(crab, aes(x = crab_or_rec, y = summer_or)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
summer_or_rec

#Neither have much of a relationship

#Adults vs. winter upwelling in CA and OR
winter_ca <- ggplot(crab, aes(x = crab_ca_ad, y = winter_ca)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
winter_ca
#negative but not too strong

winter_or <- ggplot(crab, aes(x = crab_or_ad, y = winter_or)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
winter_or
#not too strong

#Recruits vs. winter upwelling in CA and OR
winter_ca_rec <- ggplot(crab, aes(x = crab_ca_rec, y = winter_ca)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
winter_ca_rec
#not much of a relationship

winter_or_rec <- ggplot(crab, aes(x = crab_or_rec, y = winter_or)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
winter_or_rec
#also not much of a relationship
```

Barnacle densities and upwelling: 
```{r barnacle-upwelling, echo=FALSE}
#Adults vs. summer upwelling in CA and OR  
b_summer_ca <- ggplot(crab, aes(x = barnacle_ca_ad, y = summer_ca)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
b_summer_ca
#not great

b_summer_or <- ggplot(crab, aes(x = barnacle_or_ad, y = summer_or)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
b_summer_or
#not great either

#Recruits vs. summer upwelling in CA and OR
b_summer_ca_rec <- ggplot(crab, aes(x = barnacle_ca_rec, y = summer_ca)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
b_summer_ca_rec
#ehh

b_summer_or_rec <- ggplot(crab, aes(x = barnacle_or_rec, y = summer_or)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
b_summer_or_rec
#This one is strong

#Adults vs. winter upwelling in CA and OR
b_winter_ca <- ggplot(crab, aes(x = barnacle_ca_ad, y = winter_ca)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
b_winter_ca
#decently strong

b_winter_or <- ggplot(crab, aes(x = barnacle_or_ad, y = winter_or)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
b_winter_or
#not too strong

#Recruits vs. winter upwelling in CA and OR
b_winter_ca_rec <- ggplot(crab, aes(x = barnacle_ca_rec, y = winter_ca)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
b_winter_ca_rec
#not much of a relationship

b_winter_or_rec <- ggplot(crab, aes(x = barnacle_or_rec, y = winter_or)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x, se=FALSE, size=0.5) + 
  theme_bw()
b_winter_or_rec
#also not much of a relationship
```

The three relationships that seem decently strong are:  
 * OR adult crab density vs. CA recruit crab density  
 * CA adult crab densities vs. ca summer upwelling   
 * OR adult crab densities vs. or summer upwelling  
 * OR barnacle recruits vs. summer upwelling  
 * CA adult barnacles vs. winter upwelling  
 
 


