---
title: "problem_set1"
author: "Sara Orofino"
date: "1/12/2020"
output:
  pdf_document: default
  html_document: default
---
#{.tabset}
```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)

#Data:
density <- read_csv(file=file.path(here(),"density.csv"))
recruits <- read_csv(file=file.path(here(),"recruits.csv"))
```

##Question 1
###Compare and contrast changes in mean density  
Tasks:  
  - Make a column graph of mean denisty for each organism (y-axis) on both Rarotonga and Aitutaki in 2009 and 2018


```{r wrangle-density, include=FALSE}
surg <- density %>% 
  filter(organism == "surgeonfish")

trout <- density %>%
  filter(organism == "coral trout")

yellow <- density %>% 
  filter(organism == "yellow damsel")

spotted <- density %>%
  filter(organism == "spotted damsel")
```

```{r density-graphs, echo=FALSE}
#surgeonfish:
density_surg <- ggplot(surg, aes(x=location, y=density, fill = location)) + 
  geom_col(width = 0.95, alpha = 0.7) + 
  geom_errorbar(aes(ymin = density - ci, ymax = density + ci), width = 0.5) +
  facet_wrap(~year) + 
  scale_y_continuous(expand = c(0,0), limits = c(-20,450), breaks = seq(0,400,100)) + 
  scale_x_discrete(expand = c(0,0)) + 
  scale_fill_manual(name = "Island", breaks = c("Aitutaki", "Rarotonga"), values = c("dodgerblue", "darkslategray3")) +
  theme_bw() + 
  labs(y = "Mean Density of Adults (per 100 m$^2$)",
       x = "Island",
       title = "Mean Density of Surgeonfish")
density_surg

#Coral trout:
density_trout <- ggplot(trout, aes(x=location, y=density, fill = location)) + 
  geom_col(width = 0.95, alpha = 0.7) + 
  geom_errorbar(aes(ymin = density - ci, ymax = density + ci), width = 0.5) +
  facet_wrap(~year) + 
  scale_y_continuous(expand = c(0,0), limits = c(-20,200), breaks = seq(0,200,50)) + 
  scale_x_discrete(expand = c(0,0)) + 
  scale_fill_manual(name = "Island", breaks = c("Aitutaki", "Rarotonga"), values = c("dodgerblue", "darkslategray3")) +
  theme_bw() + 
  labs(y = "Mean Density of Adults (per 100 m$^2$)",
       x = "Island",
       title = "Mean Density of Coral Trout")
density_trout

#Yellow damselfish:
density_yellow <- ggplot(yellow, aes(x=location, y=density, fill = location)) + 
  geom_col(width = 0.95, alpha = 0.7) + 
  geom_errorbar(aes(ymin = density - ci, ymax = density + ci), width = 0.5) +
  facet_wrap(~year) + 
  scale_y_continuous(expand = c(0,0), limits = c(0,110), breaks = seq(0,100,25)) + 
  scale_x_discrete(expand = c(0,0)) + 
  scale_fill_manual(name = "Island", breaks = c("Aitutaki", "Rarotonga"), values = c("dodgerblue", "darkslategray3")) +
  theme_bw() + 
  labs(y = "Mean Density of Adults (per 100 m$^2$)",
       x = "Island",
       title = "Mean Density of Yellow Damselfish")
density_yellow

#Spotted damselfish:
density_spot <- ggplot(spotted, aes(x=location, y=density, fill = location)) + 
  geom_col(width = 0.95, alpha = 0.7) + 
  geom_errorbar(aes(ymin = density - ci, ymax = density + ci), width = 0.5) +
  facet_wrap(~year) + 
  scale_y_continuous(expand = c(0,0), limits = c(-35,965), breaks = seq(0,900,150)) + 
  scale_x_discrete(expand = c(0,0)) + 
  scale_fill_manual(name = "Island", breaks = c("Aitutaki", "Rarotonga"), values = c("dodgerblue", "darkslategray3")) +
  theme_bw() + 
  labs(y = "Mean Density of Adults (per 100 m$^2$)",
       x = "Island",
       title = "Mean Density of Spotted Damselfish")
density_spot
```


##Question 2
###Compare and contrast changes in density of recruits  
Tasks:  
  - Make a column graph of density of recruits for each organism on both Rarotonga and Aitutaki in 2009 and 2018


```{r wrangle-recruits, include=FALSE}
surg_r <- recruits %>% 
  filter(fish == "surgeonfish") %>% 
  filter(recruits != 0)

trout_r <- recruits %>%
  filter(fish == "coral trout") %>% 
  filter(recruits != 0)

yellow_r <- recruits %>% 
  filter(fish == "yellow damsel") %>% 
  filter(recruits != 0)

spotted_r <- recruits %>%
  filter(fish == "spotted damsel") %>% 
  filter(recruits != 0)
```

```{r recruits-graph, echo=FALSE}
#surgeonfish:
recruit_surg <- ggplot(surg_r, aes(x=location, y=recruits, fill = location)) + 
  geom_col(width = 0.95, alpha = 0.7) + 
  geom_errorbar(aes(ymin = recruits - ci, ymax = recruits + ci), width = 0.5) +
  facet_wrap(~year) + 
  scale_y_continuous(expand = c(0,0), limits = c(0,50), breaks = seq(0,50,10)) + 
  scale_x_discrete(expand = c(0,0)) + 
  scale_fill_manual(name = "Island", breaks = c("Aitutaki", "Rarotonga"), values = c("dodgerblue", "darkslategray3")) +
  theme_bw() + 
  labs(y = "Mean Density of Recruits (per m$^2$ of microhabitat)",
       x = "Island",
       title = "Mean Density of Surgeonfish Recruits")
recruit_surg

#Coral trout:
recruit_trout <- ggplot(trout_r, aes(x=location, y=recruits, fill = location)) + 
  geom_col(width = 0.95, alpha = 0.7) + 
  geom_errorbar(aes(ymin = recruits - ci, ymax = recruits + ci), width = 0.5) +
  facet_wrap(~year) + 
  scale_y_continuous(expand = c(0,0), limits = c(-1.75,15), breaks = seq(0,15,5)) + 
  scale_x_discrete(expand = c(0,0)) + 
  scale_fill_manual(name = "Island", breaks = c("Aitutaki", "Rarotonga"), values = c("dodgerblue", "darkslategray3")) +
  theme_bw() + 
  labs(y = "Mean Density of Recruits (per m$^2$ of microhabitat)",
       x = "Island",
       title = "Mean Density of Coral Trout Recruits")
recruit_trout

#Yellow damselfish:
recruit_yellow <- ggplot(yellow_r, aes(x=location, y=recruits, fill = location)) + 
  geom_col(width = 0.95, alpha = 0.7) + 
  geom_errorbar(aes(ymin = recruits - ci, ymax = recruits + ci), width = 0.5) +
  facet_wrap(~year) + 
  scale_y_continuous(expand = c(0,0), limits = c(0,52), breaks = seq(0,50,10)) + 
  scale_x_discrete(expand = c(0,0)) + 
  scale_fill_manual(name = "Island", breaks = c("Aitutaki", "Rarotonga"), values = c("dodgerblue", "darkslategray3")) +
  theme_bw() + 
  labs(y = "Mean Density of Recruits (per m$^2$ of microhabitat)",
       x = "Island",
       title = "Mean Density of Yellow Damselfish Recruits")
recruit_yellow

#Spotted damselfish:
recruit_spot <- ggplot(spotted_r, aes(x=location, y=recruits, fill = location)) + 
  geom_col(width = 0.95, alpha = 0.7) + 
  geom_errorbar(aes(ymin = recruits - ci, ymax = recruits + ci), width = 0.5) +
  facet_wrap(~year) + 
  scale_y_continuous(expand = c(0,0), limits = c(0,25), breaks = seq(0,20,5)) + 
  scale_x_discrete(expand = c(0,0)) + 
  scale_fill_manual(name = "Island", breaks = c("Aitutaki", "Rarotonga"), values = c("dodgerblue", "darkslategray3")) +
  theme_bw() + 
  labs(y = "Mean Density of Recruits (per m$^2$ of microhabitat)",
       x = "Island",
       title = "Mean Density of Spotted Damselfish Recruits")
recruit_spot
```


##Question 3
Tasks:  
  - Calculate the density of fish per 100 m2 area of reef    
  - Make a scatterplot of relationship between density of recruits and adults    
  
###Density
The density data gives the coverage of each microhabitat per 100 m$^2$ of reef. The recruitment density is per 1 m$^2$ of microhabitat. To get the density of recruits per 100 m$^2$ of reef, multiply the number of recruits by the density data number for the microhabitat.    

```{r density-calcs, include = FALSE}
####Calculate recruits by microhabitat 

##surgeonfish - fine-branching coral
#Isolate microhabitat
micro_s <- density %>% 
  filter(organism == "fine-branching corals")
#Store density
micro_density <- micro_s$density
#Add to surg density data
surg$micro_density <- micro_density
#Store density of recruits:
surg$recruits <- surg_r$recruits
#Calculate the number of recruits per 100 m2 of appropriate microhabitat
surg_calcs <- surg %>%
  mutate("recruits_100" = micro_density * recruits)


#coral trout - coarse-branching coral
#Isolate microhabitat
micro_t <- density %>% 
  filter(organism == "coarse-branching corals")
#Store density
micro_density <- micro_t$density
#Add to surg density data
trout$micro_density <- micro_density
#Store density of recruits:
trout$recruits <- trout_r$recruits
#Calculate the number of recruits per 100 m2 of appropriate microhabitat
trout_calcs <- trout %>%
  mutate("recruits_100" = micro_density * recruits)

#yellow damsel - mounding
#Isolate microhabitat
micro_y <- density %>% 
  filter(organism == "mounding corals")
#Store density
micro_density <- micro_y$density
#Add to surg density data
yellow$micro_density <- micro_density
#Store density of recruits:
yellow$recruits <- yellow_r$recruits
#Calculate the number of recruits per 100 m2 of appropriate microhabitat
yellow_calcs <- yellow %>%
  mutate("recruits_100" = micro_density * recruits)

#spotted damsel - sea anemone
#Isolate microhabitat
micro_sp <- density %>% 
  filter(organism == "sea anemones")
#Store density
micro_density <- micro_sp$density
#Add to surg density data
spotted$micro_density <- micro_density
#Store density of recruits:
spotted$recruits <- spotted_r$recruits
#Calculate the number of recruits per 100 m2 of appropriate microhabitat
spotted_calcs <- spotted %>%
  mutate("recruits_100" = micro_density * recruits)
```

```{r scatterplots, echo = FALSE}
#surgeonfish:
scatter_s <- ggplot(surg_calcs, aes(x = density, y = recruits_100)) + 
  geom_point(alpha = 0.7) + 
  geom_smooth(method = "lm", se = FALSE, color = "grey38") + 
  scale_y_continuous(expand = c(0,0), limits = c(0,85), breaks = seq(0,80,20)) +
  scale_x_continuous(expand = c(0,0.5), limits = c(0,401), breaks = seq(0,400,100)) + 
  labs(x = "Density of Adults (# per 100 m$^2$)", 
       y = "Density of Recruits (# per 100 m$^2$)", 
       title = "Surgeonfish Adult vs. Recruitment Density") +
  theme_bw()
scatter_s

#coral trout:
scatter_t <- ggplot(trout_calcs, aes(x = density, y = recruits_100)) + 
  geom_point(alpha = 0.7) + 
  geom_smooth(method = "lm", se = FALSE, color = "grey38") + 
  scale_y_continuous(expand = c(0,0), limits = c(0,40), breaks = seq(0,40,10)) +
  scale_x_continuous(expand = c(0,0.5), limits = c(0,175), breaks = seq(0,150,50)) + 
  labs(x = "Density of Adults (# per 100 m$^2$)", 
       y = "Density of Recruits (# per 100 m$^2$)", 
       title = "Coral Trout Adult vs. Recruitment Density") +
  theme_bw()
scatter_t

#yellow damsel:
scatter_y <- ggplot(yellow_calcs, aes(x = density, y = recruits_100)) + 
  geom_point(alpha = 0.7) + 
  geom_smooth(method = "lm", se = FALSE, color = "grey38") + 
  scale_y_continuous(expand = c(0,0), limits = c(0,860), breaks = seq(0,850,150)) +
  scale_x_continuous(expand = c(0,0), limits = c(30,92), breaks = seq(30,90,10)) +
  labs(x = "Density of Adults (# per 100 m$^2$)", 
       y = "Density of Recruits (# per 100 m$^2$)", 
       title = "Yellow Damselfish Adult vs. Recruitment Density") +
  theme_bw()
scatter_y

#spotted damsel: 
scatter_sp <- ggplot(spotted_calcs, aes(x = density, y = recruits_100)) + 
  geom_point(alpha = 0.7) + 
  geom_smooth(method = "lm", se = FALSE, color = "grey38") + 
  scale_y_continuous(expand = c(0,0), limits = c(0,20), breaks = seq(0,20,5)) +
  scale_x_continuous(expand = c(0,0), limits = c(0,920), breaks = seq(0,900,100)) +
  labs(x = "Density of Adults (# per 100 m$^2$)", 
       y = "Density of Recruits (# per 100 m$^2$)", 
       title = "Spotted Damselfish Adult vs. Recruitment Density") +
  theme_bw()
scatter_sp
```




##Question 4
Scatterplots of adult density (y axis) vs. density of microhabitat used by young (x axis)  

```{r density-habitat-graphs, echo=FALSE}
#surgeonfish:
scatter_s2 <- ggplot(surg_calcs, aes(x = micro_density, y = density)) + 
  geom_point(alpha = 0.7) + 
  geom_smooth(method = "lm", se = FALSE, color = "grey38") + 
  scale_y_continuous(expand = c(0,0), limits = c(0,410), breaks = seq(0,400,100)) +
  scale_x_continuous(expand = c(0,0), limits = c(0,4), breaks = seq(0,4,1)) + 
  labs(x = "Fine-Branching Coral Density (m$^2$/100 m$^2$)", 
       y = "Density of Adults (# per 100 m$^2$)", 
       title = "Microhabitat vs. Adult Surgeonfish Density") +
  theme_bw()
scatter_s2

#coral trout:
scatter_t2 <- ggplot(trout_calcs, aes(x = micro_density, y = density)) + 
  geom_point(alpha = 0.7) + 
  geom_smooth(method = "lm", se = FALSE, color = "grey38") + 
  scale_x_continuous(expand = c(0,0), limits = c(0,4), breaks = seq(0,4,1)) +
  scale_y_continuous(expand = c(0,0.5), limits = c(0,175), breaks = seq(0,150,50)) + 
  labs(x = "Coarse-Branching Coral Density (m$^2$/100 m$^2$)", 
       y = "Density of Adults (# per 100 m$^2$)", 
       title = "Microhabitat vs. Adult Coral Trout Density") +
  theme_bw()
scatter_t2

#yellow damsel:
scatter_y2 <- ggplot(yellow_calcs, aes(x = micro_density, y = density)) + 
  geom_point(alpha = 0.7) + 
  geom_smooth(method = "lm", se = FALSE, color = "grey38") + 
  scale_x_continuous(expand = c(0,0), limits = c(14,20), breaks = seq(14,20,1)) +
  scale_y_continuous(expand = c(0,0), limits = c(30,95), breaks = seq(30,90,30)) +
  labs(x = "Mounding Density (m$^2$/100 m$^2$)", 
       y = "Density of Adults (# per 100 m$^2$)", 
       title = "Microhabitat vs. Adult Yellow Damselfish Density") +
  theme_bw()
scatter_y2

#spotted damsel: 
scatter_sp2 <- ggplot(spotted_calcs, aes(x = micro_density, y = density)) + 
  geom_point(alpha = 0.7) + 
  geom_smooth(method = "lm", se = FALSE, color = "grey38") + 
  scale_x_continuous(expand = c(0,0), limits = c(0.4,2), breaks = seq(0.5,2,0.5)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,950), breaks = seq(0,900,300)) +
  labs(x = "Sea Anemone Density (m$^2$/100 m$^2$)", 
       y = "Density of Adults (# per 100 m$^2$)", 
       title = "Microhabitat vs. Adult Spotted Damselfish Density") +
  theme_bw()
scatter_sp2

```



##Question 5
Tasks:  
  - Calculate the density of adults per area of bottom covered by the microhabitat used by the young (for each lagoon and year)    
  - Graph them (similar to questions one and two)  
  
  
```{r num5-density-calcs, include=FALSE}
#surgeonfish:
surg2 <- surg_calcs %>% 
  mutate("adult_micro" = density / micro_density)

#coral trout:
trout2 <- trout %>%
  mutate("adult_micro" = density / micro_density)

#yellow damsel:
yellow2 <- yellow %>%
  mutate("adult_micro" = density / micro_density)

#spotted damsel:
spotted2 <- spotted %>% 
  mutate("adult_micro" = density / micro_density)
```

```{r num5-graphs, echo=FALSE}
#surgeonfish:
density_surg2 <- ggplot(surg2, aes(x=location, y=adult_micro, fill = location)) + 
  geom_col(width = 0.95, alpha = 0.7) + 
  facet_wrap(~year) + 
  scale_y_continuous(expand = c(0,0), limits = c(0,150), breaks = seq(0,150,50)) + 
  scale_x_discrete(expand = c(0,0)) + 
  scale_fill_manual(name = "Island", breaks = c("Aitutaki", "Rarotonga"), values = c("dodgerblue", "darkslategray3")) +
  theme_bw() + 
  labs(y = "Mean Density of Adults (per 100 m$^2$ of Fine-branching Coral)",
       x = "Island",
       title = "Density of Surgeonfish per Area of Juvenile Habitat")
density_surg2

#Coral trout:
density_trout2 <- ggplot(trout2, aes(x=location, y=adult_micro, fill = location)) + 
  geom_col(width = 0.95, alpha = 0.7) + 
  facet_wrap(~year) + 
  scale_y_continuous(expand = c(0,0), limits = c(0,55), breaks = seq(0,50,10)) + 
  scale_x_discrete(expand = c(0,0)) + 
  scale_fill_manual(name = "Island", breaks = c("Aitutaki", "Rarotonga"), values = c("dodgerblue", "darkslategray3")) +
  theme_bw() + 
  labs(y = "Mean Density of Adults (per 100 m$^2$ of Coarse-branching Coral)",
       x = "Island",
       title = "Density of Coral Trout per Area of Juvenile Habitat")
density_trout2

#Yellow damselfish:
density_yellow2 <- ggplot(yellow2, aes(x=location, y=adult_micro, fill = location)) + 
  geom_col(width = 0.95, alpha = 0.7) + 
  facet_wrap(~year) + 
  scale_y_continuous(expand = c(0,0), limits = c(0,6), breaks = seq(0,6,2)) + 
  scale_x_discrete(expand = c(0,0)) + 
  scale_fill_manual(name = "Island", breaks = c("Aitutaki", "Rarotonga"), values = c("dodgerblue", "darkslategray3")) +
  theme_bw() + 
  labs(y = "Mean Density of Adults (per 100 m$^2$ of Mounding Coral)",
       x = "Island",
       title = "Density of Yellow Damselfish per Area of Juvenile Habitat")
density_yellow2

#Spotted damselfish:
density_spot2 <- ggplot(spotted2, aes(x=location, y=adult_micro, fill = location)) + 
  geom_col(width = 0.95, alpha = 0.7) + 
  facet_wrap(~year) + 
  scale_y_continuous(expand = c(0,0), limits = c(0,525), breaks = seq(0,500,100)) + 
  scale_x_discrete(expand = c(0,0)) + 
  scale_fill_manual(name = "Island", breaks = c("Aitutaki", "Rarotonga"), values = c("dodgerblue", "darkslategray3")) +
  theme_bw() + 
  labs(y = "Mean Density of Adults (per 100 m$^2$ of Sea Anemone)",
       x = "Island",
       title = "Density of Spotted Damselfish per Area of Juvenile Habitat")
density_spot2
```


##Question 6
Tasks:  
  - Scatterplots (adult density) with trend line and r-squared value    
  - Surgeon vs. Coral Trout    
  - Surgeon vs. Yellow Damselfish    
  - Surgeon vs. Spotted Damselfish    
  - Coral Trout vs. Yellow Damselfish    
  - Coral Trout vs. Spotted Damselfish    
  - Yellow Damselfish vs. Spotted Damselfish   

```{r num6-wrangle, include=FALSE}
#Get the density counts for coral trout, yellow damsel, and spotted damsel
density_t <- trout$density
density_y <- yellow$density
density_sp <- spotted$density
#Combine with surgeonfish
surg$density_t <- density_t
surg$density_y <- density_y
surg$density_sp <- density_sp

#Combine yellow and spotted with coral trout:
trout$density_y <- density_y
trout$density_sp <- density_sp

#Combine spotted with yellow:
yellow$density_sp <- density_sp
```
  
```{r num6-plots, echo=FALSE}
##Surgeonfish on x-axis:

#vs. coral trout
scatter_st <- ggplot(surg, aes(x = density, y = density_t)) + 
  geom_point(alpha = 0.7) + 
  geom_smooth(method = "lm", se = FALSE, color = "grey38") + 
  scale_y_continuous(expand = c(0,0), limits = c(0,200), breaks = seq(0,200,50)) +
  scale_x_continuous(expand = c(0,0), limits = c(0,400), breaks = seq(0,400,100)) + 
  labs(x = "Density of Adult Surgeonfish (# per 100 m$^2$)", 
       y = "Density of Adult Coral Trout (# per 100 m$^2$)", 
       title = "Adult Surgeonfish vs. Adult Coral Trout Density") +
  theme_bw()
scatter_st

#vs. yellow damsel:
scatter_sy <- ggplot(surg, aes(x = density, y = density_y)) + 
  geom_point(alpha = 0.7) + 
  geom_smooth(method = "lm", se = FALSE, color = "grey38") + 
  scale_y_continuous(expand = c(0,0), limits = c(0,100), breaks = seq(0,100,25)) +
  scale_x_continuous(expand = c(0,0), limits = c(0,400), breaks = seq(0,400,100)) + 
  labs(x = "Density of Adult Surgeonfish (# per 100 m$^2$)", 
       y = "Density of Adult Yellow Damselfish (# per 100 m$^2$)", 
       title = "Adult Surgeonfish vs. Adult Yellow Damselfish Density") +
  theme_bw()
scatter_sy

#vs. spotted damselfish:
scatter_ssp <- ggplot(surg, aes(x = density, y = density_sp)) + 
  geom_point(alpha = 0.7) + 
  geom_smooth(method = "lm", se = FALSE, color = "grey38") + 
  scale_y_continuous(expand = c(0,0), limits = c(0,920), breaks = seq(0,900,300)) +
  scale_x_continuous(expand = c(0,0), limits = c(0,400), breaks = seq(0,400,100)) + 
  labs(x = "Density of Adult Surgeonfish (# per 100 m$^2$)", 
       y = "Density of Adult Spotted Damselfish (# per 100 m$^2$)", 
       title = "Adult Surgeonfish vs. Adult Spotted Damselfish Density") +
  theme_bw()
scatter_ssp

##Coral Trout on x-axis 
#vs. yellow damselfish:
scatter_ty <- ggplot(trout, aes(x = density, y = density_y)) + 
  geom_point(alpha = 0.7) + 
  geom_smooth(method = "lm", se = FALSE, color = "grey38") + 
  scale_y_continuous(expand = c(0,0), limits = c(0,100), breaks = seq(0,100,25)) +
  scale_x_continuous(expand = c(0,0), limits = c(0,200), breaks = seq(0,200,50)) + 
  labs(x = "Density of Adult Coral Trout (# per 100 m$^2$)", 
       y = "Density of Adult Yellow Damselfish (# per 100 m$^2$)", 
       title = "Adult Coral Trout vs. Adult Yellow Damselfish Density") +
  theme_bw()
scatter_ty

#vs. spotted damselfish:
scatter_tsp <- ggplot(trout, aes(x = density, y = density_sp)) + 
  geom_point(alpha = 0.7) + 
  geom_smooth(method = "lm", se = FALSE, color = "grey38") + 
  scale_y_continuous(expand = c(0,0), limits = c(0,920), breaks = seq(0,900,300)) +
  scale_x_continuous(expand = c(0,0), limits = c(0,200), breaks = seq(0,200,50)) + 
  labs(x = "Density of Adult Coral Trout (# per 100 m$^2$)", 
       y = "Density of Adult Spotted Damselfish (# per 100 m$^2$)", 
       title = "Adult Coral Trout vs. Adult Spotted Damselfish Density") +
  theme_bw()
scatter_tsp

##yellow damselfish on the x-axis
#vs. spotted damselfish:
scatter_ysp <- ggplot(yellow, aes(x = density, y = density_sp)) + 
  geom_point(alpha = 0.7) + 
  geom_smooth(method = "lm", se = FALSE, color = "grey38") + 
  scale_y_continuous(expand = c(0,0), limits = c(0,920), breaks = seq(0,900,300)) +
  scale_x_continuous(expand = c(0,0), limits = c(25,100), breaks = seq(0,100,25)) + 
  labs(x = "Density of Adult Yellow Damselfish (# per 100 m$^2$)", 
       y = "Density of Adult Spotted Damselfish (# per 100 m$^2$)", 
       title = "Adult Yellow Damselfish vs. Adult Spotted Damselfish Density") +
  theme_bw()
scatter_ysp
```

