---
title: "problem_set1"
author: "Sara Orofino"
date: "1/12/2020"
output: html_document
---
#{.tabset}
```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)

#Data:
density <- read_csv(file=file.path(here(),"density.csv"))
recruits <- read_csv(file=file.path(here(),"recruits.csv"))
```

##Question 1
###Compare and contrast changes in mean density  
Tasks:  
  - Make a column graph of mean denisty for each organism (y-axis) on both Rarotonga and Aitutaki in 2009 and 2018


```{r wrangle-density, include=FALSE}
surg <- density %>% 
  filter(organism == "surgeonfish")

trout <- density %>%
  filter(organism == "coral trout")

yellow <- density %>% 
  filter(organism == "yellow damsel")

spotted <- density %>%
  filter(organism == "spotted damsel")
```

```{r density-graphs, echo=FALSE}
#surgeonfish:
density_surg <- ggplot(surg, aes(x=location, y=density, fill = location)) + 
  geom_col(width = 0.95, alpha = 0.7) + 
  geom_errorbar(aes(ymin = density - 32, ymax = density + 32), width = 0.5) +
  facet_wrap(~year) + 
  scale_y_continuous(expand = c(0,0), limits = c(-20,450), breaks = seq(0,400,100)) + 
  scale_x_discrete(expand = c(0,0)) + 
  scale_fill_manual(name = "Island", breaks = c("Aitutaki", "Rarotonga"), values = c("dodgerblue", "darkslategray3")) +
  theme_bw() + 
  labs(y = "Mean Density of Adults (per 100 m$^2$)",
       x = "Island",
       title = "Mean Density of Surgeonfish")
density_surg

#Coral trout:
density_trout <- ggplot(trout, aes(x=location, y=density, fill = location)) + 
  geom_col(width = 0.95, alpha = 0.7) + 
  geom_errorbar(aes(ymin = density - 21, ymax = density + 21), width = 0.5) +
  facet_wrap(~year) + 
  scale_y_continuous(expand = c(0,0), limits = c(-20,200), breaks = seq(0,200,50)) + 
  scale_x_discrete(expand = c(0,0)) + 
  scale_fill_manual(name = "Island", breaks = c("Aitutaki", "Rarotonga"), values = c("dodgerblue", "darkslategray3")) +
  theme_bw() + 
  labs(y = "Mean Density of Adults (per 100 m$^2$)",
       x = "Island",
       title = "Mean Density of Coral Trout")
density_trout

#Yellow damselfish:
density_yellow <- ggplot(yellow, aes(x=location, y=density, fill = location)) + 
  geom_col(width = 0.95, alpha = 0.7) + 
  geom_errorbar(aes(ymin = density - 15, ymax = density + 15), width = 0.5) +
  facet_wrap(~year) + 
  scale_y_continuous(expand = c(0,0), limits = c(0,110), breaks = seq(0,100,25)) + 
  scale_x_discrete(expand = c(0,0)) + 
  scale_fill_manual(name = "Island", breaks = c("Aitutaki", "Rarotonga"), values = c("dodgerblue", "darkslategray3")) +
  theme_bw() + 
  labs(y = "Mean Density of Adults (per 100 m$^2$)",
       x = "Island",
       title = "Mean Density of Yellow Damselfish")
density_yellow

#Spotted damselfish:
density_spot <- ggplot(spotted, aes(x=location, y=density, fill = location)) + 
  geom_col(width = 0.95, alpha = 0.7) + 
  geom_errorbar(aes(ymin = density - 47, ymax = density + 47), width = 0.5) +
  facet_wrap(~year) + 
  scale_y_continuous(expand = c(0,0), limits = c(-35,965), breaks = seq(0,900,150)) + 
  scale_x_discrete(expand = c(0,0)) + 
  scale_fill_manual(name = "Island", breaks = c("Aitutaki", "Rarotonga"), values = c("dodgerblue", "darkslategray3")) +
  theme_bw() + 
  labs(y = "Mean Density of Adults (per 100 m$^2$)",
       x = "Island",
       title = "Mean Density of Spotted Damselfish")
density_spot
```


##Question 2
###Compare and contrast changes in density of recruits  
Tasks:  
  - Make a histogram of density of recruits for each organism on both Rarotonga and Aitutaki in 2009 and 2018


##Question 3



##Question 4




##Question 5



##Question 6